### 2019-06-07 dmtcs_submission.d/symmetry_properties.tex
ssr

\noindent
\textbf{Example 6:}
Consider the Boolean function $f$ of four variables, 
namely $a$, $b$, $c$ and $d$,
whose truth table is shown in Table~\ref{tab:not_str_ssym_ex}.
Function $f$ is symmetric under the permutation $cdab$.
For convenience, we give the truth table for $f$ in a form
that makes its symmetry under the permutation $cdab$ clear.
We now argue that the function is
not pairwise symmetric for any pair of variables.

@@

\noindent
\begin{minipage}{0.05\textwidth}
\hspace*{0.08in}
\end{minipage}
\begin{minipage}{0.85\textwidth}
\begin{description}
\item{(i)} $f(0100) \neq f(1000)$, so $a$ and $b$ are not symmetric.
\item{(ii)} $f(0011) \neq f(1001)$, so $a$ and $c$ are not symmetric.
\item{(iii)} $f(0001) \neq f(1000)$, so $a$ and $d$ are not symmetric.
\item{(iv)} $f(0100) \neq f(0010)$, so $b$ and $c$ are not symmetric.
\item{(v)} $f(0011) \neq f(0110)$, so $b$ and $d$ are not symmetric.
\item{(vi)} $f(0001) \neq f(0010)$, so $c$ and $d$ are not symmetric.
\end{description}
\end{minipage}

@@

\begin{table}[tb]
\begin{center}
\begin{tabular}{|l|l|c||l|l|c|}\hline
$a~b$ & $c~d$ & $f$ & $a~b$ & $c~d$ & $f$ \\ \hline\hline
0~0 & 0~1 & 0 & 0~1 & 1~1 & 1 \\ \hline
0~1 & 0~0 & 0 & 1~1 & 0~1 & 1  \\ \hline
0~0 & 1~0 & 1 & 1~0 & 1~1 & 1 \\ \hline
1~0 & 0~0 & 1 & 1~1 & 1~0 & 1 \\ \hline
0~0 & 1~1 & 0 & 0~0 & 0~0 & 0 \\ \hline
1~1 & 0~0 & 0 & 0~1 & 0~1 & 0 \\ \hline
0~1 & 1~0 & 1 & 1~0 & 1~0 & 0 \\ \hline
1~0 & 0~1 & 1 & 1~1 & 1~1 & 0 \\ \hline
\end{tabular}
\end{center}
\caption{An Example of a Boolean Function which is
properly $n$-symmetric but not strongly asymmetric.}
\label{tab:not_str_ssym_ex}
\end{table}

>>>>

\noindent
\textbf{Example 6:}
Consider the Boolean function $f$ of four variables, 
namely $a$, $b$, $c$ and $d$,
whose truth table is shown in Table~\ref{tab:not_str_ssym_ex}.
Function $f$ is symmetric under the permutation $cdab$.
For convenience, we give the truth table for $f$ in a form
that makes its symmetry under the permutation $cdab$ clear.
So, the function $f$ is not strongly asymmetric.
We now demonstrate that the function is properly $4$-symmetric
by observing that it is not symmetric with respect to any pair of variables.

@@

\noindent
\begin{minipage}{0.01\textwidth}
%\hspace*{0.03in}
\end{minipage}
\begin{minipage}{0.85\textwidth}
\begin{description}
\item{(i)} $f(0100) \neq f(1000)$, so $a$ and $b$ are not symmetric.
\item{(ii)} $f(0011) \neq f(1001)$, so $a$ and $c$ are not symmetric.
\item{(iii)} $f(0001) \neq f(1000)$, so $a$ and $d$ are not symmetric.
\item{(iv)} $f(0100) \neq f(0010)$, so $b$ and $c$ are not symmetric.
\item{(v)} $f(0011) \neq f(0110)$, so $b$ and $d$ are not symmetric.
\item{(vi)} $f(0001) \neq f(0010)$, so $c$ and $d$ are not symmetric.
\end{description}
\end{minipage}

@@

\begin{table}[tb]
\begin{center}
\begin{tabular}{|l|l|c||l|l|c|}\hline
$a~b$ & $c~d$ & $f$ & $a~b$ & $c~d$ & $f$ \\ \hline\hline
0~0 & 0~1 & 0 & 0~1 & 1~1 & 1 \\ \hline
0~1 & 0~0 & 0 & 1~1 & 0~1 & 1  \\ \hline
0~0 & 1~0 & 1 & 1~0 & 1~1 & 1 \\ \hline
1~0 & 0~0 & 1 & 1~1 & 1~0 & 1 \\ \hline
0~0 & 1~1 & 0 & 0~0 & 0~0 & 0 \\ \hline
1~1 & 0~0 & 0 & 0~1 & 0~1 & 0 \\ \hline
0~1 & 1~0 & 1 & 1~0 & 1~0 & 0 \\ \hline
1~0 & 0~1 & 1 & 1~1 & 1~1 & 0 \\ \hline
\end{tabular}
\end{center}
\caption{An example of a Boolean function with 4 variables which is
properly $4$-symmetric but not\newline strongly asymmetric.}
\label{tab:not_str_ssym_ex}
\end{table}
